The Minimal Retroreflective Microfacet Model

### 2025-12-23 MRM.tex
Correct author name.
Typo fix.

\author{Matthias Raab\\NVIDIA
        \and Laurent Belcour\\Intel
        \and Frankie Liu\\NVIDIA
        \and Jamie Portsmouth\\Autodesk
       }

@@

Figure~\ref{fig:data_fit} shows a fit of the retroreflective MRM model (in red) to the measured BRDF of retroreflective tape (in blue) from \cite{BelcourBackvector}. This is the "yellow tape" sample from their dataset, illuminated at three different light source angles $\theta_L \in \{15^\circ, 30^\circ, 60^\circ\}$ (in the plane of incidence).  The MRM model provides a reasonably good match to the retroreflective peak using a roughness of $r = 0.23$, together with ``F82-tint'' Fresnel \cite{OpenPBR2024} with $F_0=0.19$ and $F_{82} = 0$.

>>>>

\author{Matthias Raab\\NVIDIA
        \and Laurent Belcour\\Intel
        \and Francis Liu\\NVIDIA
        \and Jamie Portsmouth\\Autodesk
       }

@@

Figure~\ref{fig:data_fit} shows a fit of the retroreflective MRM model (in red) to the measured BRDF of retroreflective tape (in blue) from \cite{BelcourBackvector}. This is the ``yellow tape'' sample from their dataset, illuminated at three different light source angles $\theta_L \in \{15^\circ, 30^\circ, 60^\circ\}$ (in the plane of incidence).  The MRM model provides a reasonably good match to the retroreflective peak using a roughness of $r = 0.23$, together with ``F82-tint'' Fresnel \cite{OpenPBR2024} with $F_0=0.19$ and $F_{82} = 0$.
